Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-29 latex/comp_or.tex
Finished Comp OR paper

Table \ref{tab:ground} presents the distances minimization of the next node destined pallets to the ramp door. Columns {\bf Before} and {\bf After} refer to the application of the current method. In average, the distances from the pallets and the last ramp door position was diminished by 5\% along a tour.

@@

Another important discovery is that the relaxed version of the MIP solver followed by the multiprocessing 3D packing yielded efficient solutions, even a little bit faster than {\it mpShims} (Table \ref{tab:results2}), but not surpassing {\it mpShims}' quality results.

>>>>

Table \ref{tab:ground} presents the distances minimization of the next node destined pallets to the ramp door. Columns {\bf Before} and {\bf After} refer to the application of the current method. On average, the distances from the pallets and the last ramp door position was diminished by 5\% along a tour.

@@
